Automated Formal Synthesis of Safe Digital Controllers\\ for Continuous Plants

### 2018-05-10 automatica/paper.tex
section 8

@@

We separate our evaluation into two sets of results: fixed- and floating-point. 
For the majority of the fixed-point benchmarks, we observe that the abstraction-based
back-end is faster than the basic multi-staged verification approach, and
finds one solution more (14) than the multi-staged back-end (13).  In direct
comparison, the abstraction-based approach is on average able to find a
solution in approximately 53\% of the time required using the multi-staged
back-end, and has a median run-time 0.5\,s, which is twenty times smaller
than the multi-staged approach.  The two back-ends complement each other in
benchmark coverage and together solve 58\% of the benchmarks.
%
For the majority of the floating-point benchmarks, we also observe that the abstraction-based
back-end is much faster than the basic multi-staged verification approach, but both
back-ends find the same amount of solutions (13).  In direct
comparison, the abstraction-based approach is on average able to find a
solution in approximately 50\% of the time required using the multi-staged
back-end, and has a median run-time 0.6\,s, which is forty times smaller
than the multi-staged approach.  The two back-ends complement each other in
benchmark coverage and together solve 54\% of the benchmarks.

@@

The median run-time for our benchmark set is 6.6\,s for fixed-point and 5.45\,s for floating-point. 
We consider these times short enough to be of practical use to control engineers, and thus affirm EG1.

There are a few instances for which the system fails to find a controller. 
For the na\"ive approach, the completeness threshold may be too large, thus
causing a timeout.  On the other hand, the abstraction-based approach may
require a very precise abstraction, resulting in too many refinements and,
consequently, in a timeout.  Yet another source of incompleteness is the
inability of the {\sc synthesize} phase to use a large enough precision for
the plant model.

@@

@@

\textcolor{red}{Cristina: Can you please write an initial version of the conclusions?}

>>>>

\note{Perhaps rather than `safety check' we could speak about robustness to changes in sampling time.}

@@

We separate our evaluation into two sets of results: fixed- and floating-point. 
For the majority of the {\it fixed-point} benchmarks, we observe that the abstraction-based
back-end is faster than the basic multi-staged verification approach, and
finds a solution for more benchmarks (14) than the multi-staged back-end (13) \note{we should clarify that this is out of 26 in total, not 191?}.  
In direct comparison, the abstraction-based approach is on average able to find a
solution in approximately 53\% of the time required using the multi-staged
back-end, and has a median run-time 0.5\,s, which is twenty times smaller
than the multi-staged approach.  The two back-ends complement each other in terms of 
benchmark coverage, and together solve 58\% of the benchmarks \note{only? this does not sound much really}.  
%
For the majority of the benchmarks with {\it floating-point} implementation, 
we also observe that the abstraction-based back-end is much faster than the basic multi-staged verification approach, 
but both back-ends find the same amount of solutions (13).  
In direct comparison, the abstraction-based approach is on average able to find a
solution in approximately 50\% of the time required using the multi-staged
back-end, and has a median run-time 0.6\,s, which is forty times smaller
than the multi-staged approach.  The two back-ends complement each other in
benchmark coverage and together solve 54\% of the benchmarks \note{somewhat underwhelming}.

@@

The median run-time for \note{the successful} benchmarks is 6.6\,s for the fixed-point and 5.45\,s for floating-point implementations, respectively.  
We consider these times short enough to be of practical use to control engineers, and thus affirm the validity of EG1.

There are \note{a few [you mean half!]} instances for which both approaches fail to synthesise a controller.  
For the multi-stage approach, the completeness threshold may be too large, thus causing a timeout.  
On the other hand, the abstraction-based approach may require a very precise abstraction, resulting in too many refinements and, consequently, again in a timeout.  
Yet another source of incompleteness is the inability of the {\sc synthesize} phase to use a large enough precision for
the plant model.

@@

\note{So, what about EG2? Shall we assert it? }

@@

We have presented two automated approaches to synthesize digital
state-feedback controllers that ensure both stability and safety over state-space models.   
The first approach relies on unfolding of the closed-loop model dynamics up to a completeness threshold, while the second
one applies abstraction-refinement and acceleration to increase speed, whilst retaining soundness.
%
Both approaches are novel within the control literature: they give a fully
automated synthesis method that is algorithmically and numerically sound,
considering various error sources in the implementation of the digital
control algorithm and in the computational modeling of plant dynamics.
%
Our experimental results show that both approaches are able to synthesize fully automatically 
safe controllers for most benchmarks, which have been derived from the control literature, 
within a reasonable amount of time.

\note{Let us collect here the main extensions we regard to be relevant: \\ 
models with partial observations; \\ 
implementation with SMT; \\ 
continuous-time; \\ 
more complex specs; \\ 
\ldots }
